Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-09-28 RegReport/paper.tex
Added osf url to paper
Update paper.tex

\begin{figure}[t]
  \centering  
  %\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_prior_plot.pdf}}
  %\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:exp1_strategy}
\end{figure}

@@

\begin{enumerate}
\item There is a difference (in either direction) in search behaviour between those participants who pre-crastinated and those who did not. This will be determined by looking at \textcolor{red}{$p(\lvert \delta \rvert >0.05 | X)$. A value >0.95 will be taken as evidence of a difference.} 
\item The magnitude of the difference is in-line with the value of 0.125 ($95\%$ HPDI of $[-0.003, 0.242]$) obtained in our pilot experiment. This will be determined by comparing the new HPDI with the pilot HPDI. A new estimate for the size of the difference will then be computed by pooling all data in a mixed-effect model (with random effects for data collected in Aberdeen, Essex, and Pilot).
\item There is a positive correlation ($r=0.22$) between pre-crastination and conscientiousness.
\end{enumerate}

@@

The task replicates that used in \cite{fournier2019task}, in which participants were instructed to pick up two buckets and place them on the crates behind the start position. We will closely follow the methods and instructions as described in their appendix. Each participant will complete three trials before the visual search task, and three trials after. While the experimenter is setting up the buckets for the next trial, the participant will be asked to walk over to a nearby window and look outside until they are asked to return. The full protocol and instructions given to participants is available at <insert url here>.

>>>>

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_prior_plot.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:exp1_strategy}
\end{figure}

@@

\begin{enumerate}
\item There is a difference (in either direction) in search behaviour between those participants who pre-crastinated and those who did not. This will be determined by looking at $p(\delta>0 | X)$. A value <0.05 will be taken as evidence that pre-crastination leads to less optimal search strategies, while a value >0.95 will be taken as evidence for the opposite.
\item The magnitude of the difference is in-line with the value of 0.125 ($95\%$ HPDI of $[-0.003, 0.242]$) obtained in our pilot experiment. This will be determined by comparing the new HPDI with the pilot HPDI. A new estimate for the size of the difference will then be computed by pooling all data in a mixed-effect model (with random effects for data collected in Aberdeen, Essex, and Pilot).
\item There is a positive correlation ($r=0.22$) between pre-crastination and conscientiousness.
\end{enumerate}

@@

The task replicates that used in \cite{fournier2019task}, in which participants were instructed to pick up two buckets and place them on the crates behind the start position. We will closely follow the methods and instructions as described in their appendix. Each participant will complete three trials before the visual search task, and three trials after. While the experimenter is setting up the buckets for the next trial, the participant will be asked to walk over to a nearby window and look outside until they are asked to return. The full protocol and instructions given to participants is available at https://osf.io/5aq4c/.
